
% surveys and articles of interst ffor this litterature review
%   https://arxiv.org/pdf/1907.09358.pdf
%   https://arxiv.org/pdf/1206.5538.pdf
%   https://medium.com/radix-ai-blog/representation-learning-breakthroughs-what-is-representation-learning-5dda2e2fed2e




Maybe include the notion of deep learning?


% Litterature review on representation learning
%   lacks sources
Representation learning has become a hugely adopted method under deep learning and fearure learning. Representation learning has shown promising results in various areas. In computervision, it has become standard to use Convolutional Neural Networks (CNN) to learn representations of images and more. In Natural language processing, word embeddings have become standard to represent words as vectors. Also transformers shows huge potential. E.g. Bert








One of the first articles to present the concept of \textit{Machine Unlearning} was in \cite{cao_towards_2015}. 








Could potentially include existing representation learning in other fields (computer-vision, text-data). Papers of interest:
\begin{itemize}
    \item BERT 
\end{itemize}
Could include existing representatino learning for time-series. Papers of interest:
\begin{itemize}
    \item TS2VEC: First paper to perform contrastive learning in a hierarchical way over augmented frames
    \item First paper to use transformers to generate representations https://arxiv.org/pdf/2010.02803.pdf
    \item 
\end{itemize}
Could include Current implemented Machine UnLearning techniques. Papers of interest:
\begin{itemize}
    \item 
\end{itemize}


